Clustering in a hyperbolic model of complex networks.

### 2020-03-11 paper.tex

\title{Clustering in a hyperbolic model of complex networks.}
\author[1]{Nikolaos Fountoulakis\thanks{Research partially supported by the Alan Turing Institute, grant no. EP/N510129/1.}}
\author[2]{Pim van der Hoorn\thanks{Research partially supported by ARO Grant W911NF-16-1-0391 and W911NF-17-1-0491}}
\author[3]{Tobias M\"{u}ller\thanks{Research partially supported by NWO grants 639.032.529 and 612.001.409.}}
\author[3]{Markus Schepers\thanks{Research partially supported by NWO grant 639.032.529.}}

\affil[1]{ School of Mathematics, University of Birmingham, United Kingdom.}
\affil[2]{Department of Physics, Northeastern University, United States.}
\affil[3]{Bernoulli Institute, University of Groningen, The Netherlands.}

@@

Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form 
expression in terms of $\alpha, \nu$ and certain special functions. 
This improves earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero 
with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that 
$c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit 
$\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. 
We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. 
Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$. 
More precisely, there exists constants $c_{\alpha,\nu}$ depending on $\alpha$ and $\nu$, such that as $k \to \infty$, 
$\gamma(k) \sim c_{\alpha,\nu} \cdot k^{2 - 4\alpha}$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, 
$\gamma(k) \sim c_{\alpha,\nu} \cdot \log(k) \cdot k^{-1} $ 
if $\alpha=\frac{3}{4}$ and $\gamma(k) \sim c_{\alpha,\nu} \cdot k^{-1}$ when $\alpha > \frac{3}{4}$. 
These results contradict a conjecture of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale 
with $k^{-1}$ as we let $k$ grow. 
\end{abstract}

@@

>>>>

\title{Clustering in a hyperbolic model of complex networks.}
\author[1]{Nikolaos Fountoulakis\thanks{Research partially supported by the Alan Turing Institute, grant no. EP/N510129/1.}}
\author[2,3]{Pim van der Hoorn\thanks{Research partially supported by ARO Grant W911NF-16-1-0391 and W911NF-17-1-0491}}
\author[4]{Tobias M\"{u}ller\thanks{Research partially supported by NWO grants 639.032.529 and 612.001.409.}}
\author[4]{Markus Schepers\thanks{Research partially supported by NWO grant 639.032.529.}}

\affil[1]{ School of Mathematics, University of Birmingham, United Kingdom.}
\affil[2]{Department of Mathematics and Computer Science, Eindhoven University of Technology, The Netherlands}
\affil[3]{Department of Physics, Northeastern University, United States.}
\affil[4]{Bernoulli Institute, University of Groningen, The Netherlands.}

@@

Here we show that the clustering coefficient tends in probability to a constant $\gamma$ that we give explicitly as a closed form 
expression in terms of $\alpha, \nu$ and certain special functions. 
This improves earlier work by Gugelmann et al., who proved that the clustering coefficient remains bounded away from zero 
with high probability, but left open the issue of convergence to a limiting constant. Similarly, we are able to show that 
$c(k)$, the average clustering coefficient over all vertices of degree exactly $k$, tends in probability to a limit 
$\gamma(k)$ which we give explicitly as a closed form expression in terms of $\alpha, \nu$ and certain special functions. 
We are able to extend this last result also to sequences $(k_n)_n$ where $k_n$ grows as a function of $n$. 
Our results show that $\gamma(k)$ scales differently, as $k$ grows, for different ranges of $\alpha$. 
More precisely, there exists constants $c_{\alpha,\nu}$ depending on $\alpha$ and $\nu$, such that as $k \to \infty$, 
$\gamma(k) \sim c_{\alpha,\nu} \cdot k^{2 - 4\alpha}$ if $\frac{1}{2} < \alpha < \frac{3}{4}$, 
$\gamma(k) \sim c_{\alpha,\nu} \cdot \log(k) \cdot k^{-1} $ 
if $\alpha=\frac{3}{4}$ and $\gamma(k) \sim c_{\alpha,\nu} \cdot k^{-1}$ when $\alpha > \frac{3}{4}$. 
These results contradict a claim of Krioukov et al., which stated that the limiting values $\gamma(k)$ should always scale 
with $k^{-1}$ as we let $k$ grow. 
\end{abstract}

@@

%=======
%\TM{ Maybe a ``conclusion and further work'' section here,  before the references and appendix?}
%
%\section{Conclusion and further work}
%
%??
%>>>>>>> Stashed changes

### 2020-03-11 proofs_finite_k.tex

\begin{corollary}\label{cor:NGPok} 
For every fixed $k\geq 0$ we have

@@

\noindent
(The case $k=0$ follows from all the other cases together with the fact that the $\pmf(k)$ sum to one.)

@@

\begin{corollary}\label{cor:GPoHdegseq}
For every fixed $k$ we have

@@

By Theorem~\ref{thm:mainkfixed} and~\eqref{eq:gugeldegseqaap} we have, for any fixed $K\geq 2$:

>>>>

\begin{corollary}\label{cor:NGPok} 
For every fixed $k\geq 1$ we have

@@

@@

\begin{corollary}\label{cor:GPoHdegseq}
For every fixed $k \geq 1$ we have

@@

By Theorem~\ref{thm:mainkfixed} and~\eqref{eq:gugeldegseqaap} we have, for any fixed $k\geq 2$:
